Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-06 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] bug fix for low-q^2 predictions in Table 4, lower q^2-boundary now 1.1 GeV^2 (before 1)
[draft-tensor-op] minor modifications Intro and Fig 1 caption

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,.
\end{align}
LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the angular
distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term $F_H^\mu$
in CP-averaged form and integrated over several bins in the dilepton invariant
mass $q^2$. Similarly, the CP-averaged branching ratios, ${\cal B}_\mu =
\tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling
    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
    observables are rescaled by the lifetime of the $B$ meson,
    $\tau_B$. The bands represent the theory uncertainties at 68\% and
    95\% probability of the prior predictive.  Two sets of bands are
    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
    (red). If available, the gray band indicates the latest 68\%
    confidence interval reported by LHCb.}
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline
  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
  & --
  & 1
  & 1
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The posterior predictive 68\% probability intervals of not-yet-measured
     angular observables for several new-physics scenarios given all the
     considered experimental constraints. The corresponding values for the
     SM (prior predictive) are given, too, where ``$\simeq 0$'' indicates
     zero in the considered approximation, see text for details.
   }
\end{table*}

>>>>

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,.
\end{align}
LHCb analyzed their full run 1 data set of 3 fb$^{-1}$ and measured the angular
distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
\mu$~\cite{Aaij:2014tfa}, with unprecedented precision. They provide the
lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term $F_H^\mu$
in CP-averaged form and integrated over several bins in the dilepton invariant
mass $q^2$. Similarly, the CP-averaged branching ratios, ${\cal B}_\mu =
\tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling
    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
    \bar\mu\mu$. All observables are integrated over $q^2 \in [q_1^2,\,q_2^2]$
    bins denoted as
    $\langle \dots \rangle_{[q^2_1,\, q^2_2]}$. Angular
    observables are rescaled by the lifetime of the $B$ meson,
    $\tau_B$. The bands represent the theory uncertainties at 68\% and
    95\% probability of the prior predictive.  Two sets of bands are
    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
    (red). If available, the gray band indicates the latest 68\%
    confidence interval reported by LHCb.}
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.6_{-1.9}^{+1.8}) \cdot 10^{-9\;}$
  & $(-0.1_{-1.9}^{+2.3}) \cdot 10^{-10}$
  & $(0.2_{-1.1}^{+1.1}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.30_{-0.56}^{+0.65}) \cdot 10^{-9\;}$
  & $(4.8_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.6_{-0.4}^{+0.5}) \cdot 10^{-9\;}$
  & $(2.8_{-1.1}^{+1.5}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.44_{-0.48}^{+0.46}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.0_{-1.2}^{+1.6}) \cdot 10^{-10}$
  & $(1.5_{-1.1}^{+1.0}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline
  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
  & --
  & 1
  & 1
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The posterior predictive 68\% probability intervals of not-yet-measured
     angular observables for several new-physics scenarios given all the
     considered experimental constraints. The corresponding values for the
     SM (prior predictive) are given, too, where ``$\simeq 0$'' indicates
     zero in the considered approximation, see text for details.
   }
\end{table*}
